The Design and Implementation of the Synchronous Language \CEU

### 2016-10-01 paper.tex
(>) 200ms huge tick

In Section~\ref{sec.ceu.exts}, we argue that event occurrences are 
infinitesimal and can never be absolutely simultaneous.
However, the ``sensation of simultaneity'' is not infinitesimal, but actually 
increases with the inaccuracy of the observer (e.g., a human being).
Therefore, we consider that simultaneity should be defined case by case, and 
should not be imposed by the language.
%
First-class timers simplify the implementation of application-defined 
simultaneity.
%
Figure~\ref{lst.simultaneous} emulates a \code{middle\_click} event (ln. 3) in 
terms of ``simultaneous'' occurrences of \code{LEFT\_CLICK} and 
\code{RIGHT\_CLICK} (ln. 1--2).
If both events occur, we emit the internal event \code{middle\_click} (ln.  
6--7).
However, if one of them occurs and the \emph{200ms} timer expires (ln. 9--10), 
we abort the whole behavior with the \code{par/or} (ln. 5) and try again with 
the enclosing \code{loop} (ln. 4).
%
In this specification, ``simultaneous'' means ``within 200 milliseconds'', 
which is a huge amount of time for a language-defined tick.
%, and which would break the synchronous hypothesis.
%
For instance, a similar implementation of this specification in Esterel would 
not rely on the tick notion of simultaneity either.
%
%Conversely, an environment for \CEU could provide \code{TICK} input and 
%broadcast it periodically to allow applications to recover the abstract notion 
%of simultaneity (e.g., changing ln. 10 to \code{await TICK}).
%the expiring event from \code{200ms} to \code{TICK} in ln.  10).

>>>>

In Section~\ref{sec.ceu.exts}, we argue that event occurrences are 
infinitesimal and can never be absolutely simultaneous.
However, the ``sensation of simultaneity'' is not infinitesimal, but actually 
increases with the inaccuracy of the observer (e.g., a human being).
Therefore, we consider that simultaneity should be defined case by case, and 
should not be imposed by the language.
%
First-class timers simplify the implementation of application-defined 
simultaneity.
%
Figure~\ref{lst.simultaneous} emulates a \code{middle\_click} event (ln. 3) in 
terms of ``simultaneous'' occurrences of \code{LEFT\_CLICK} and 
\code{RIGHT\_CLICK} (ln. 1--2).
If both events occur, we emit the internal event \code{middle\_click} (ln.  
6--7).
However, if one of them occurs and the \emph{200ms} timer expires (ln. 9--10), 
we abort the whole behavior with the \code{par/or} (ln. 5) and try again with 
the enclosing \code{loop} (ln. 4).
%
In this specification, ``simultaneous'' means ``within 200 milliseconds'', 
which might be a huge amount of time for a language-defined tick.
%, and which would break the synchronous hypothesis.
%
For instance, an implementation of this specification in Esterel would be
similar, since it would not rely on the tick notion of simultaneity either.
%
%Conversely, an environment for \CEU could provide \code{TICK} input and 
%broadcast it periodically to allow applications to recover the abstract notion 
%of simultaneity (e.g., changing ln. 10 to \code{await TICK}).
%the expiring event from \code{200ms} to \code{TICK} in ln.  10).
